%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Technical Expert - Perception \textbar\ Tracking} % Job title
    {Robert Bosch LLC} % Organization
    {Hybrid \textbar\ Plymouth, MI} % Location
    {Jan. 2024 - Present} % Date(s)
    {
    }
  \\\cventrytitle
    {Senior Software Engineer - Perception \textbar\ Tracking} % Job title
    {} % Organization
    {} % Location
    {Sep. 2018 - Jan. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as a technical lead for a global Perception / Tracking software team.}
        \item {Secured a strategic acquistion through realizing tracking gains brought by architectural changes for a 5 radar 1 video configuration.}
        \item {Optimized radar-based perception for a new generation of radar sensor.}
        \item {Developed several new features for MATLAB-based tracking visualization tooling, including projection of the components of the Kalman filter, and automation abilities.}
        \item {Coordinated with cross-functional software teams and management to determine long term planning of software content and integration strategies.}
        \item {Supported and led critical customer demos and meetings, even outside of my main area of expertise.}
        \item {Acted as Product Owner for an Agile System-of-Systems team.}
        \item {Developed Python-based KPI Tool for single target tracking analysis, integrated and automated its execution as a Jenkins pipeline.}
        \item {Increased performance of corner radar-based tracking (C++) by identifying and addressing assumptions made towards front-facing radars.}
        \item {Reworked object type classification feature calculations to be more agnostic of sensor-mounting, reducing missed-target scenarios.}
        \iflongform        
          \item {Facilitated first deployment of tracking code on a new ECU, with a new middleware.}
          \item {Adapted MATLAB-based object type classifier training tool for corner use-cases.}
          \item {Tripled Jenkins simulation throughput through determining bottleneck in execution.}
        \fi
        % \item {Root-caused an irreproducible plant issue, satisfying the customer's concerns regarding reoccurence.}
        % \item {Implemented Python-based suite of tools to ease the handling of MF4 measurements for re-simulation purposes.} 
        % \item {Coached a student team through the development of a video-based automated labelling tool to reduce validation effort.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer - Predictive Safety Systems} % Job title
    {Bosch Engineering North America} % Organization
    {Farmington Hills, MI} % Location
    {Apr. 2016 - Sep. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as the Predictive Safety System (AEB, FCW, System Conditioning) Component Responsible for a strategic customer.}
        \item {Developed Python-based data mining tools to open new opportunities in evaluating data sets from endurance runs.}
        \item {Introduced automated tooling to enable customer-friendly overviews for endurance run points of interest.}
        \item {Led labelling sessions with the customer, explaining and addressing concerns with any activations.}
        % \item {Analyzed and addressed false negatives and false positives from endurance runs and NHTSA use-case tests by proposing tuning trade-offs with the customer.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {} % Location
    {Apr. 2012 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed unique solution for criticality classification for marine radar collision warning applications, modified tracking and localization logic to be less dependent on traffic scenes.}
        \item {Designed and implemented Python-based code generation tool chain to allow a Bosch-created library to be integrated into a third-party controller.}
        \item {Served as diagnostic Component Responsible and integrator in Electronic Power Steering (EPS) and EBCM projects.}
        \item {Led a global diagnostic communication software development team, coordinating tasks and workloads.}
        \iflongform     
        \item {Created an ABS simulation software (C-based) and testing client (in CANAPE/CAPL) for OEM brake component testing, greatly reducing the OEM endurance run effort.}
        \item {Integrated ASIL-D control functions in EPS unit, to facilitate level three functions, the first for that product generation.}
        \item {Identified and documented previously unknown errata in Bosch-provided tool chain, and in a third-party provide compiler.}
        \item {Reduced EBCM software-release effort through automations and improvements made to tools.}
        \item {Integrated a third-party Simulink model into a Electronic Brake Control Module (EBCM), the first such integration for that generation of product.}
        \item {Coached student team through the development of a mobile app to allow easy reflashing and retuning of EBCMs.}
        \fi
      \end{cvitems}
      % \item {Supported customers on site in solving critical plant issues.} % relatively redundant
      % \item {Network and diagnostic communication Component Responsible for multiple EPS and EBCM projects; configured, implemented, and tested several CAN and diagnostic stacks (J1939, UDS) in C.} % relatively redundant
    }
%---------------------------------------------------------
\end{cventries}
